### 2015-01-12 mcmc.tex
reordering of the sections, some guide at the beginning

@@

MCMC methods are proven to be correct ``in the limit''; that is, when
an infinite number of samples have been taken.
When the function $f(\pars)$ has challenging properties, the results
can approach this limit very slowly (or not at all\note{HOGG: discuss
  situations in which MCMC will not work---related to support.}).
For this reason, in the finite duration of a scientific project, most
users of MCMC have one of two (related) problems:
Either \textsl{(1)}~it is taking too long---it is taking too many steps or
executing too many calls of the function $f(\pars)$ to get independent samples---or \textsl{(2)}~it is not
exploring the full parameter space---there are local optima (or bad
local geometry around those optima) ``trapping'' the algorithm.

>>>>

In what follows, we are going to provide a kind of ``user manual'' or
advice document or folklore capture regarding the use of MCMC for
data analysis.
This will not be a detailed description of multiple MCMC methods
(indeed, we will only explain one method in detail), and it will not
be about the mathematical properties or structure of the method or
methods.
It will be about how to use MCMC, including diagnosis and
trouble-shooting.

The first couple of \sectionname s will describe what a sampling is, and how
the simplest MCMC method, the Metropolis-Hastings algorithm, can
provide one.
The next few \sectionname s will provide ideas about how to
initialize, tune and operate MCMC methods for good performance.
The last few \sectionname s will provide advice for making decisions
among the myriad MCMC methods implementations, how to implement a good
likelihood function and prior pdf function for inference, and how to
trouble-shoot standard kinds of problems that arise in operating MCMC
methods on real problems.
We will leave parenthetical and philosophical matters to the end-notes,
which appear after the main text.

@@

As we have discussed above, MCMC methods are proven to be correct ``in the limit''; that is, when
an infinite number of samples have been taken.
When the function $f(\pars)$ has challenging properties, the results
can approach this limit very slowly (or not at all\note{HOGG: discuss
  situations in which MCMC will not work---related to support.}).
For this reason, in the finite duration of a scientific project, most
users of MCMC have one of two (related) problems:
Either \textsl{(1)}~it is taking too long---it is taking too many steps or
executing too many calls of the function $f(\pars)$ to get independent samples---or \textsl{(2)}~it is not
exploring the full parameter space---there are local optima (or bad
local geometry around those optima) ``trapping'' the algorithm.
